
---
title: "Sample vs. Population Approach"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
   

---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```


```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r, echo=FALSE}
xaringanExtra::use_webcam()
```

```{r xaringan-fit-screen, echo=FALSE}
xaringanExtra::use_fit_screen()
```

---
class: inverse, center, middle

# Research Questions

We have a research question and we want to find data to answer it. 

---
class: center, inverse, middle
# Research Question 1

---
# Research Question 1

- The average GPA for students at four-year colleges in the US is around 3.15. Are Bryant students class of 2025 doing better than an average college student?

---
# The "Population" approach: 

- Collect the current GPA of ALL Bryant students class 2025. This data is called population data. 

- Calculate the average of the collected GPA. 

- Compare the calculated average with 3.15 to answer the research question. 

---
# The "Sample" Approach: 

- Collect the current GPA of SOME Bryant students class 2025. This data is called sample data.  

- Use hypothesis testing technique to answer the research question

---
# Pros and Cons

- Which approach has a more "accurate" answer? Population approach

- It's possible that the population data already exists (at the registrar office for example) and The researcher may be able to get access to this data. 

- If you can collect the population data, you should not use the "Sample" approach. 

---
class: center, inverse, middle
# Research Question 2

---
# Research Question 2

- There is different between current freshman and senior students at Bryant on the number of hours they spend to study. 

---
# "Population" Approach 

- Collect the number of hours spent for studying a week of ALL current Bryant students. 

- Calculate the average of number of hours for freshman and senior 

- Compare the calculated average to answer the research question. 

---
# "Sample" Approach: 

- Collect the current GPA of SOME Bryant students class 2025. This data is called sample data.  

- Use hypothesis testing technique to answer the research question

---
# Pros and Cons

- The population data very likely do not exist.  The researcher needs to manually collect the data  

- The researcher needs to ask about 1000 freshmen and 1000 seniors at Bryant. 

- Sample approach provide a better solution:  The researcher just needs to ask about 30 freshmen and 30 seniors. Then use hypothesis testing technique to reach the answer.  

---
class: center, inverse, middle
# Population and Variables of a research question

Research Question: College students who has higher sleep quality tends to achieve higher education performances. 

Population: All college students 
Variable of study: 

