
---
title: "Different Sampling Techniques"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
   

---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

```{r xaringan-tile-view, echo=FALSE}
xaringanExtra::use_tile_view()
```


```{r xaringan-panelset, echo=FALSE}
xaringanExtra::use_panelset()
```

```{r, echo=FALSE}
xaringanExtra::use_webcam()
```

```{r xaringan-fit-screen, echo=FALSE}
xaringanExtra::use_fit_screen()
```

---
class: inverse, center, middle

# Hypothesiss

We have a hypothesis and we want to find data to test it. 

---
class: center, inverse, middle
# Hypothesis 1

The average GPA for students at four-year colleges in the US is around 3.15. Hypothesis: Bryant students class of 2025 are doing better than an average college student.

---
# The "Population" approach: 

- Collect the current GPA of ALL Bryant students class 2025. This data is called population data. 

- Calculate the average of the collected GPA. 

- Compare the calculated average with 3.15 to test the hypothesis. 

---
# The "Sample" Approach: 

- Collect the current GPA of SOME Bryant students class 2025. This data is called sample data.  

- Use statistics technique to test the hypothesis

---
# Pros and Cons

- Which approach give us a more "accurate" test? Population approach!

- It's possible that the population data already exists (at the registrar office for example) and The researcher may be able to get access to this data. 

- If you can collect the population data, you should not use the "Sample" approach. 

---
class: center, inverse, middle
# Hypothesis 2

Bryant freshman students study more hours than Bryant senior students.

---
# "Population" Approach 

- Collect the number of hours spent for studying a week of ALL current Bryant students. 

- Calculate the average of number of hours for freshman and senior 

- Compare the calculated average to test the hypothesis. 

---
# "Sample" Approach: 

- Collect the current GPA of SOME Bryant students class 2025. This data is called sample data.  

- Use statistics technique to test the hypothesis

---
# Pros and Cons

- The population data very likely do not exist.  The researcher needs to manually collect the data  

- The researcher needs to ask about 1000 freshmen and 1000 seniors at Bryant. 

- "Sample" approach provide a better solution:  The researcher just needs to ask about 30 freshmen and 30 seniors. Then use statistics technique to reach the test.  

---
class: center, inverse, middle
# Hypothesis 3

College students who has better sleep quality achieve higher education performances.

---

- Hypothesis: College students who has better sleep quality achieve higher education performances.

- Population: All college students in the world.  This is a very large population that is not easy to get the data from. 

- The researcher should collect only a portion of college students then use statistics technique to answer the question. 

---
# Examples on The "Sample" approach

https://journals.sagepub.com/doi/abs/10.2466/pr0.96.3.817-824?journalCode=prxa

https://www.researchgate.net/profile/Mussie-Tessema/publication/271077619_Tessema_M_Ready_K_Astanie_M_2014_Does_Part-Time_Job_Affect_College_Students'_Satisfaction_and_Academic_Performance_GPA_The_Case_of_a_Mid-sized_Public_University_International_Journal_of_Business_Admin/links/57769e4408aead7ba071cf1e/Tessema-M-Ready-K-Astanie-M-2014-Does-Part-Time-Job-Affect-College-Students-Satisfaction-and-Academic-Performance-GPA-The-Case-of-a-Mid-sized-Public-University-International-Journal-of-Business.pdf

https://www.businessinsider.com/could-your-gpa-predict-your-income-2014-4


